Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-07-15 analysis/paper/sim_survey_paper.Rmd
Minor modification of the correlation in simulation

```{r data, include = FALSE}
library(SimSurvey)
library(plotly)
library(raster)
library(lattice)
library(viridis)
library(data.table)
load("analysis/cod_sim_exports/2018-07-07_test/test_output.RData")
```

@@

which_year <- 7
which_sim <- 4

@@

d <- sim$age_strat_error
d <- d[d$survey == which_survey & d$sim %in% 1:1000, ]
d$age[d$age > 8] <- 8 # aggregate beyond 10
d$age <- as.character(d$age)
d$age[d$age == "8"] <- "8+"
d$age <- factor(d$age, levels = c(as.character(1:7), "8+"))
d <- d[, list(I_hat = sum(I_hat), I = sum(I)), by = c("year", "age", "sim")]

@@

which_set_dens <- c(0.0005, 0.002, 0.01)
which_len_caps <- c(10, 100, 1000)
which_year <- 5

@@

which_set_dens <- c(0.0005, 0.002, 0.01)
which_len_caps <- c(10, 100, 1000)
which_age <- 6

@@

>>>>

```{r data, include = FALSE}
library(SimSurvey)
library(plotly)
library(raster)
library(lattice)
library(viridis)
library(data.table)
load("analysis/cod_sim_exports/2018-07-13_test/test_output.RData")
```

@@

which_year <- 7
which_sim <- 1

@@

d <- sim$age_strat_error
d <- d[d$survey == which_survey & d$sim %in% 1:10, ]
d$age[d$age > 8] <- 8 # aggregate beyond 10
d$age <- as.character(d$age)
d$age[d$age == "8"] <- "8+"
d$age <- factor(d$age, levels = c(as.character(1:7), "8+"))
d <- d[, list(I_hat = sum(I_hat), I = sum(I)), by = c("year", "age", "sim")]

@@

which_set_dens <- c(0.0005, 0.002, 0.01)
which_len_caps <- c(10, 100, 1000)
which_year <- 7

@@

which_set_dens <- c(0.0005, 0.002, 0.01)
which_len_caps <- c(10, 100, 1000)
which_age <- 4

@@

```{r tot-fig, fig.width = 7, fig.height = 3}

which_set_dens <- c(0.0005, 0.002, 0.01)
which_len_caps <- c(10, 100, 1000)

d <- merge(sim$surveys, sim$total_strat_error, by = "survey")
d <- d[d$set_den %in% which_set_dens & 
         d$lengths_cap == 100 & d$ages_cap == 10, ] ## length and age sampling not a factor here

## quantiles for fan plot
quants <- seq(90, 10, by = -10)
ints <- lapply(quants, function(q) {
  d[, list(prob = paste0(q, "%"),
           lower = quantile(I_hat, prob = (1 - q / 100) / 2),
           upper = quantile(I_hat, prob = 1 - (1 - q / 100) / 2)), 
    by = c("year", "set_den")]
})
ints <- rbindlist(ints)
ints$prob <- factor(ints$prob, levels = paste0(quants, "%"))

cols <- viridis::viridis(3)
ggplot(data = ints) + 
  geom_ribbon(aes(x = year, ymin = lower, ymax = upper, fill = prob, alpha = prob)) +
  geom_line(aes(x = year, y = I), data = d, color = cols[1], size = 1) +
  scale_fill_viridis(name = "Pr", discrete = TRUE, begin = 0.1) +
  scale_alpha_discrete(name = "Pr") + 
  facet_wrap(~ set_den, nrow = 1) +
  xlab("Year") + ylab("Abundance index") +
  theme_minimal() +
  scale_y_continuous(labels = format_si()) +
  scale_x_continuous(expand = c(0.01, 0)) +
  guides(color = guide_legend(keywidth = 0.4, keyheight = 0.25, 
                              default.unit = "cm", ncol = 1)) +
  theme(legend.justification = c(0, 1),
        plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "cm"))
